A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-14 text/informal-overview.tex
Fix a bug.
Add the example of vadd function to Section 2.

Third, we also need type equivalence rules in \LMD because its type system contains dependent types.
For example, vadd function, which takes a length of vector and returns addition function for vectors with the length, is following.
\newcommand{\M}{\textrm{M}}
\newcommand{\I}{\textrm{Int}}
\newcommand{\Vn}{\text{Vector}\ (\%_\alpha n)}
\begin{align*}
	  & \textbf{let}\ \text{vadd}_1 : \Pi n:\I.\TW_\alpha\Vn\to\TW_\alpha\Vn\to\TW_\alpha\Vn                 \\
	  & \hspace{7mm} = \textbf{fix}\ f.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vn.\ \lambda v_2:\TW_\alpha\Vn. \\
	  & \hspace{14mm} \textbf{if}\ n = 0                                                                     \\
	  & \hspace{14mm} \textbf{then} \TB_\alpha \text{nil}                                                    \\
	  & \hspace{14mm} \textbf{else}\ \TB_\alpha (                                                            \\
	  & \hspace{21mm} \textbf{let}\ t_1 = \text{tail}\ (\TBL_\alpha v_1)\ \textbf{in}                        \\
	  & \hspace{21mm} \textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}                        \\
	  & \hspace{21mm} \text{cons}\ (\text{head}\ t_1 + \text{head}\ t_2) (\TBL_\alpha f\ (n-1)\ t_1\ t_2))   \\
\end{align*}
\begin{align*}
	  & \textbf{let}\ \text{vadd}_\alpha : \Pi n:\I.\TW_\alpha(\Vn\to\Vn\to\Vn)                                                                      \\
	  & \hspace{7mm} = \lambda n:\I.\TB_\alpha (\lambda v_1:\Vn.\ \lambda v_2:\Vn. \TBL_\alpha \text{vadd}_1\ n\ (\TB_\alpha v_1)\ (\TB_\alpha v_2)) \\
\end{align*}
Although there are new primitives relating to stages which aren't in \LLF,
we can design all rules except \QPercent\ easily.
\red{design?}
\red{この段落が短い。後ろとくっつけてもいいが、段落の趣旨がボケる。}

% Q-% rule

The biggest problem in extension is handling the CSP symbol $\%_\alpha$ in \LMD.
The equivalence simple rule to handle CSP is \QCsp.
\begin{center}
	\infrule{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}}{\QCsp}
\end{center}
However, this rule isn't enough when the parameters of dependent types are cross-staed.
We will discuss this problem in a later section and solve this problem with the new rule \QPercent.
\begin{center}
	\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
\end{center}
\red{この段落でQ-Cspの持つ問題点を指摘すべきか? ただ、ここでmulmatの例を使うと3章と被る。}

>>>>

Third, we also need type equivalence rules in \LMD because its type system contains dependent types.
Although there are new primitives relating to stages which aren't in \LLF,
we can design all rules except \QPercent\ easily from the syntax or the reductions of \LMD.

\QPercent\ is different from other rules because it was designed from practical reason, not from the syntax or the reductions.
For example, we discuss $\text{vadd}_\beta$ function,
which takes a length of vector and returns addition function for vectors with the length.
$\text{vadd}_1$ is a helper function to make $\text{vadd}$, 
which takes a stage, a length of vectors, and two quoted vectors and returns a quoted vector.
\newcommand{\Vpn}{\text{Vector}\ (\%_\alpha n)}
\begin{align*}
	  & \textbf{let}\ \text{vadd}_1 : \F\alpha.\Pi n:\I.\TW_\alpha\Vpn\to\TW_\alpha\Vpn\to\TW_\alpha\Vpn                 \\
	  & \hspace{7mm} = \textbf{fix}\ f.\Lambda\alpha.\lambda n:\I.\ \lambda v_1:\TW_\alpha\Vpn.\ \lambda v_2:\TW_\alpha\Vpn. \\
	  & \hspace{14mm} \textbf{if}\ n = 0                                                                     \\
	  & \hspace{14mm} \textbf{then} \TB_\alpha \text{nil}                                                    \\
	  & \hspace{14mm} \textbf{else}\ \TB_\alpha (                                                            \\
	  & \hspace{21mm} \textbf{let}\ t_1 = \text{tail}\ (\TBL_\alpha v_1)\ \textbf{in}                        \\
	  & \hspace{21mm} \textbf{let}\ t_2 = \text{tail}\ (\TBL_\alpha v_2)\ \textbf{in}                        \\
	  & \hspace{21mm} \text{cons}\ (\text{head}\ t_1 + \text{head}\ t_2) (\TBL_\alpha f\ (n-1)\ t_1\ t_2))   \\
\end{align*}
Using $\text{vadd}_1$, we can make $\text{vadd}$ function easily.
This function takes the length of vectors and returns a quoted add function for vector of the given size.
\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta n)}
\begin{align*}
	  & \textbf{let}\ \text{vadd}: \Pi n:\I.\F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)          \\ 
	  & \hspace{7mm} = \lambda n:\I.\Lambda\beta.\TB_\beta (\lambda v_1:\Vpn.\ \lambda v_2:\Vpn. \\
	  & \hspace{63mm} \TBL_\beta \text{vadd}_1\ \beta\ n\ (\TB_\beta\ v_1)\ (\TB_\beta\ v_2))      \\
\end{align*}
\renewcommand{\Vpn}{\text{Vector}\ (\%_\beta 10)}
When we use this function, we need to instantiate $\text{vadd}$ with a length.
If we instantiate it with a integer 10, we get function $\text{vadd10}$ whose type is \\
$\text{vadd10}: \F\beta.\TW_\beta(\Vpn\to\Vpn\to\Vpn)$.
This function is difficult to use because its type contains $\Vpn$.
In most cases, we have vectors of type $\text{Vector}\ 10$, not $\Vpn$.
Therefore, we want to identify $\text{Vector}\ 10$ and $\Vpn$.

In order to resolve this problem, we introduced \QPercent into \LMD.
\QPercent\ enables us to identify $\text{Vector}\ 10$ and $\Vpn$.
This rule says that if term $M$ has the same type at stage $A\alpha$ and $A$,
we can assume $\%_\alpha M \E M$ which roughly means $\%_\alpha M$ and $M$ are equivalent.
With this rule, we can identify $10$ and $\%_\beta 10$ and use $\text{vadd}$ to many vectors.
\begin{center}
	\infrule{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}{\QPercent}
\end{center}
